\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\title{ChatBox AI \\ \Large User Manual and README}
\author{Your Name}
\date{\today}

\begin{document}
\maketitle

\section{Project Overview}
ChatBox AI is a web-based AI chat assistant designed to help students ask questions about coursework, planning, and general topics in a conversational format. This manual describes how the hypothetical system is intended to be used and how it would be installed and run in a real deployment.

\section{Jira Link}
All project tasks, epics, and sprint planning for the course are tracked in Jira.

\noindent\textbf{Jira Board:} \url{https://your-jira-link-here.com} % <-- replace with real link

\section{Objectives and Goals}
\begin{itemize}
  \item Provide a simple and intuitive chat interface for students.
  \item Demonstrate how an AI-backed web application can be structured using modern tools.
  \item Document the full software lifecycle using SDD, SRS, design spec, and testing reports.
\end{itemize}

\section{Why This Software Matters}
AI chat systems are becoming standard tools for learning and productivity. This project simulates how a university-focused AI assistant could help students:
\begin{itemize}
  \item Ask quick conceptual questions.
  \item Plan study schedules.
  \item Get reminders about deadlines (in future extensions).
\end{itemize}

\section{How to Download or Access}
In this course project, the focus is on documentation rather than a fully running system. In a real deployment, the following steps would be used:

\subsection*{Clone the Repository}
\begin{verbatim}
git clone https://github.com/your-username/chatbox-ai-docs.git
cd chatbox-ai-docs
\end{verbatim}

\subsection*{Docker-Based Deployment (Conceptual)}
\begin{enumerate}[label=\arabic*.]
  \item Install Docker and docker-compose.
  \item Set up environment variables (e.g., database credentials, AI API key).
  \item Run: \texttt{docker-compose up --build}
  \item Open a web browser and navigate to: \texttt{http://localhost:8080}
\end{enumerate}

\section{User Guide}

\subsection{Student User Flow}
\begin{enumerate}[label=\arabic*.]
  \item Open the ChatBox AI website.
  \item Create an account or log in.
  \item Start a new chat session.
  \item Type a question into the chat box and press \emph{Send}.
  \item Read the AI response and continue the conversation.
  \item Optionally, revisit past sessions or export the conversation (Snapshot 2 feature).
\end{enumerate}

\subsection{Admin User Flow}
\begin{enumerate}[label=\arabic*.]
  \item Log in as an admin user.
  \item Open the \emph{Admin Dashboard}.
  \item Review usage statistics and system health indicators.
\end{enumerate}

\section{Limitations and Future Work}
\begin{itemize}
  \item Real AI integration would require secure handling of API keys.
  \item Future work includes better personalization, reminders, and integration with learning management systems.
\end{itemize}

\end{document}
